### 2019-06-18 README.Rmd
Fix reference tables
Also:
 - Complete yeast_analysis.R script

 - Update bibliography

 - Fix `plot_venn` function
Adjust main README.md

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

@@

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

The compendium includes all the data, code, and text associated with the publication.
It is structured as an R package to facilitate reproducilibity and distribution.
The principles and motivations behind using research compendiums for academic 
research is detailed in [Marwick et al. (2017)](https://doi.org/10.1080/00031305.2017.1375986).

@@

@@

```
    .
    ├── /R                   # Script files containing reused functions
    ├── /analysis            # Full analysis report and scripts
    ├── /data                # Raw, cleaned, external, and results data
    ├── /manuscript          # Final manuscript and associated files
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # R markdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

@@

### How to cite

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/csdaw/candidaev/archive/master.zip>

Or you can install this compendium as an R package `candidaev` from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("csdaw/candidaev")
```
### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>")
```

@@

![GitHub last commit](https://img.shields.io/github/last-commit/csdaw/candidaev.svg?style=popout)

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Sur7 family proteins are putative markers for
_Candida albicans_ extracellular vesicles. Mol. Cell. Proteomics, submitted.

It has been permanently archived at Zenodo with the DOI shown above.

The compendium includes all the data, code, and text associated with the 
publication. It is structured as an R package to facilitate reproducilibity and 
distribution. The principles and motivations behind using research compendiums 
for academic research is detailed in 
[Marwick et al. (2018)](https://doi.org/10.1080/00031305.2017.1375986).

@@

### Citation

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Research compendium for: _Sur7 family proteins are_
_putative markers for_ Candida albicans _extracellular vesicles_, 2019. 
Version x.x.x. Zenodo. URL.

@@

```
    .
    ├── /R                   # Script files for functions and included data
    ├── /data-raw            # Raw data used (but not modified) in analyses
    ├── /data                # Data tables installed with package
    ├── /inst/manuscript     # Final submitted manuscript and supplemental files
    ├── /man                 # Auto-generated documentation for functions and included data
    ├── /vignettes           # Detailed examples of how analyses were performed
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitattributes       # List of files for github/linguist to ignore
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # R markdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

@@

### Accessing the compendium

#### 1. Downloading directly from GitHub
You can download the compendium as a zip from from this URL: 
<https://github.com/csdaw/candidaev/archive/master.zip>. 
Note that the contents of `/data-raw` is not installed when the package is 
installed but instructions for downloaded just these files is provided
[here](https://github.com/csdaw/candidaev/tree/master/data-raw).

#### 2. Cloning via `git`

#### 3. Installing the package using R and `devtools`

This research compendium can be installed as an R package `candidaev` from 
GitHub using `devtools`:
```{r gh-install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("csdaw/candidaev")
```

### Using the `candidaev` package

### R session information

The system on which this document was compiled was running 
pandoc v`r rmarkdown::pandoc_version()`. Here is output of 
`sessionInfo()`.

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
